---
title: "visualization"
author: "Ruihan Ding"
date: "2025-09-25"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
library(p8105.datasets)
```

Import the weather data.

```{r}
data("weather_df")
```

Making our first plot.

```{r}
ggplot(weather_df, mapping = aes(x = tmin, y = tmax)) +
  geom_point()

```

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()

```

```{r}
ggp_weather_scatterplot = 
  weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()

ggp_weather_scatterplot

```

Check that some rows are missing.

```{r}
weather_df |> 
  filter(is.na(tmax))

```

## Fancier scatterplot

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = 0.3) +
  geom_smooth(se = FALSE)

```

Where you define aesthetics can matter

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name), alpha = 0.3, size = 0.8) +
  geom_smooth(se = FALSE)

```

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name, size = prcp), alpha = 0.3) +
  geom_smooth(se = FALSE)

```

Use facetting real quick

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name), alpha = 0.3, size = 0.8) +
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)  ## row ~ column

```

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name), alpha = 0.3, size = 0.8) +
  geom_smooth(se = FALSE) +
  facet_grid(name ~ .)

```

Let's make a somewhat interesting scatterplot.

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax, color = name, shape = name)) +
  geom_point(aes(size = prcp), alpha = 0.3) +
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)

```

Learning Assessment 1

```{r}
weather_df |> 
  filter(name == "CentralPark_NY") |>   ## REMEMBER HOW TO FILTER!!
  mutate(
    tmax_fah = tmax * (9 / 5) + 32,
    tmin_fah = tmin * (9 / 5) + 32
  ) |> 
  ggplot(aes(x = tmin_fah, y = tmax_fah)) +
  geom_point() +
  geom_smooth(se = FALSE, method = "lm")

```

## Small Things

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax, color = name, shape = name)) +
#  geom_point(alpha = 0.3) +
  geom_smooth(se = FALSE) 

weather_df |> 
  ggplot(aes(x = tmin, y = tmax, color = name, shape = name)) +
  geom_smooth(se = FALSE) +
  geom_point()
```

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_hex()

```

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(color = "purple")

weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(color = "#086bfd")
```

## Univariate plots

```{r}
weather_df |> 
  ggplot(aes(x = tmin)) +
  geom_histogram(color = "white", fill = "red")

```

```{r}
weather_df |> 
  ggplot(aes(x = tmin, color = name)) +
  geom_histogram()

weather_df |> 
  ggplot(aes(x = tmin, fill = name)) +
  geom_histogram()

```

How would I fix this? Maybe facet?

```{r}
weather_df |> 
  ggplot(aes(x = tmin, fill = name)) +
  geom_histogram() +
  facet_grid(name ~ .)

```

Maybe a demsity plot?

```{r}
weather_df |> 
  ggplot(aes(x = tmin, fill = name)) +
  geom_density(alpha = 0.2)

```

```{r}
weather_df |> 
  ggplot(aes(x = name, y = tmin)) +
  geom_boxplot(aes(fill = name))

```

violin plots

```{r}
weather_df |> 
  ggplot(aes(x = name, y = tmin, fill = name)) +
  geom_violin()

```

ridge plots

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = name, fill = name)) +
  geom_density_ridges()

```

LA Univariate plots

Learning Assessment 2

```{r}
weather_df |> 
  ggplot(aes(x = prcp, fill = name)) +
  geom_density()

weather_df |> 
  ggplot(aes(x = prcp, fill = name)) +
  geom_histogram() +
  facet_grid(name ~ .)

weather_df |> 
  filter(prcp > 5, prcp < 1000) |> 
  ggplot(aes(x = prcp, fill = name)) +
  geom_density()

```

```{r}


```

## Saving and embedding plots

saving plots

```{r}
ggp_weather = 
  weather_df |> 
  ggplot(aes(x = name, y = tmin, fill = name)) +
  geom_violin()

ggp_weather

ggsave("plots/violin_plot.pdf", ggp_weather,
       width = 8, height = 6)   ## These are optional (width & height)

```

embedding plots

```{r, fig.width = 6, fig.height = 4}

ggp_weather

```



